Parametric controls on vegetation responses to biogeochemical forcing in the CLM5

### 2019-07-05 referee_responses.tex

In this paper Fisher et al. explore the sensitivity of CLM5's vegetation responses to assumed parameters in relation to the nitrogen cycle. Overall the paper is very thorough, clearly written and sets out to achieve its objectives. I do have a series of small suggestions (below) and a few larger suggestions. which I would outline here.

\textsf{AR: Thanks for the positive comments. We hope this version is somewhat easier to digest}

1. (Classic reviewer here - sorry) Whilst the paper does do what it said it would, I can't help thinking this paper could be more interesting if it presented the analysis in a slightly different way. Feel free to ignore all of this!

\textsf{AR: Noted...}

This paper documents three new assumptions (arguably four- section 2.1.4 as well) to CLM5 related to N; however, it doesn't give much consideration to these hypotheses, instead focussing on a broader list of impacts related to parameter choice. After reading the methods, what I was expecting (hoping) to see, was what impact these different assumptions would have on carbon fluxes. I was then expecting to see the impact of the underlying params from *these schemes (assumptions)* being probed. That isn't what we get from this paper and (my bias) I feel like this is an opportunity missed. I found it hard to interpret the impact of parameters (semi)divorced from the underlying structural assumptions. Moreover, many of the params (in my eyes) had little to do with the new code additions. For example, a lot of text is devoted to exploring the sensitivity to the Medlyn slope parameter. To me, this feels out of scope for what this paper should(could) be.

\textsf{AR: We appreciate the disconnect between the parameter choice being seemingly unrelated to the lengthy discussion of the new nitrogen cycling elements of the model. On further reflection,  we determined that our overall aim is to illustrate how the C and N responses of the model are impacted by parameter choice, given their large implications for carbon cycle feedback analysis. We think this is of slightly greater interest to a wider audience than specifically probing the differences between the CLM4.5 and CLM5 N cycle, although the two are related.  While many of the elements that affect the CO$_{2}$ and N responses are linked to the new model structure, there are several parameters that have large impacts which are not. In the new version of the manuscript, we have chosen to reduce the amount of text devoted to the specific changes to the N cycle, and instead to shift the focus slightly such that we are now looking specifically at how parameters affect the fertilization responses. Parameters of the new model components are included specifically to illustrate their impact. }

\textsf{An alternative approach would be to run the simulations with the various pieces of code turned off and returned to the default state. The problem with implementing that idea is that large changes of that type tended to modify the system state.  Therefore there are impacts on the fertilization responses solely because the initial system state was moved to conditions that were more or less light saturated, and more or less limited by water or nitrogen. (indeed, this is one of the main conclusions of the analysis). Further, with the exception of the LUNA code, technically it is quite difficult to turn off and on the FUN and FlexCN options without invoking other more poorly documented post CLM4.5 modifications, thus we have taken the approach of exploring the behaviour of the new models by modifying their major controlling parameters.}

@@

So, my suggestion here would be to show the impact of each of the 3(4) new assumptions in relation to how nutrients are treated with CLM5 and then to explore how sensitive those results were to the underlying params. Here, my expectation was that in some cases the results would be insensitive, but in others, it is clear that the notion of a single PFT value does not make sense. As I understand it, the authors varied the gs slope term based on the param range in my 2015 paper. This gives them some erroneous results, but that wouldn't be unexpected as using the C3 grass param (a "spendy" plant) in an arid environment wouldn't make biophysical sense?

\textsf{AR: We agree with this idea wrt. the range of variation across PFTs perhaps being excessively wide. We have now modified the stomatal slope range to use the standard error reported in Table 2 of de Kauwe et al. 2015. This does notably reduce the impact of the Medlyn slope parameter on the analysis, and remove some of the more interesting feedbacks on water limitation that the wider range had illustrated, but maybe that's just how it has to be.}

@@

In my opinion the editor shouldn't impose such a change on the authors as it is potentially a lot of work and not what they wished their paper to be about. It is just my suggestion. Equally, I would have loved to have seen those N hypotheses tested at the Duke/Oak Ridge FACE experiments, perhaps that is for another paper :P.

\textsf{AR: For the sake of full disclosure, we did actually run the model for those sites, but for reasons that are unclear, we got very low LAI predictions, and therefore extremely sensitive responses to fertilization. We thought in the end that fixing up the model to perform better at those particular sites was less interesting than the overall controls over the response to CO$_{2}$ and N forcing.}

@@

2. At the very least, I think the number of params considered should be streamlined. Many feel a bit irrelevant and there is a lot of text devoted to each. Whilst I appreciate the lengths the authors have gone to explaining the impact in the results, I found myself drifting because at times it felt out of scope. I think reducing the number considered (even moving N to the supplementary) would make the paper more readable.

\textsf{AR: We agree here, and have as a result removed 5 of the 13 parameters that had limited impacts on the fertilization responses. We have also made efforts to streamline the remaining results text, and we hope the new text is not such a trial to get through (concurring that the first version was challenging in this respect). }

@@

3. The manuscript makes a number of citations to CLM papers in review. In many places these references add little to the paper as they provide no detail and I can't look the paper up (obviously at some point soon I will be able to). My sense is that the paper would benefit from either expanding the text in some places or removing the reference entirely. For example, the Kennedy plant hydraulics paper was referenced on five occasions, that seems excessive to me given the paper is on nitrogen. This might seem like I'm being pedantic, but honestly it breaks the readability of the text.

\textsf{AR: The MS is part of a special issue, and so all the papers should become available at the same time (except the Kennedy paper which is already published). We have reduced the number of citations for the Kennedy paper down to two. The primary resource we cite is the CLM5 tech note, which is already online but will also become an appendix to the Lawrence et al. paper when these papers are all published simultaneously. Across the special issue, this is our overall strategy to documenting the entirety of the model, and we wanted to avoid duplicating large amounts of the technical text in different places.}

@@

4. Whilst I wholeheartedly agree that assessing the model simulations against observations doesn't necessarily indicate skill, it does go a bit against the grain the way the authors have presented their results. The plots as presented are quite abstract and the authors may consider this point in revision. As a reviewer, it wouldn't bother me at all if the model seemingly performed worse with added "realism", particularly if the authors could explain why.

\textsf{AR: Fair point, but 1) you may be an atypical reviewer and 2) we still think this would distract from the main purpose of the paper, which is to document and explain the differential sensitivities of the parameter ensemble to CO$_{2}$ and N fertilization. If we added in specific site data, readers would almost certainly focus on the model fit to particular sites, which we anticipate will be explored in future literature. Nonetheless, the plots are a little abstract. We have tried to improve the presentation of the results by consolidating the number of plots, putting all of the state outputs into the same figure, adding a new figure focused on the time-dependant responses of the default model, and }

@@

5. Finally, with the discussion I'm reading this as a non-CLM user and thinking what can I take away here? Here I struggled a little bit if I'm honest. There is some interesting text about objective calibration (great to be able to cite this :P), but again I'm wondering if this is really in the scope? Six paragraphs are devoted to apparent limitations - seems excessive, there is more to sell here than criticise? I think other modelling groups who haven't yet implemented these hypotheses in relation to the representation of the N cycle could learn a great deal from a paper like this. I'd ask the authors to reflect on what they think the messages they'd like to portray are and see if they feel those messages are in the discussion.

\textsf{AR: We concur that this aspect was difficult to ascertain from the original text, and so have re-written the discussion section with a view to including clearer digestion of the findings, and also a specific section on which parts of the analysis may and may not be applicable to models other than CLM5. We also reduced the scope of the limitations section to balance out weighting of the discussion.}

@@

Minor stuff (Key points/Abstract/Intro/Methods): 
------------------------------------------------

- Could the second key point be written in more readable English? In the third key point N has not been defined. Also, fertilisation of what (presumably CO2? But it could be nitrogen...or anything). Finally, "other important parameters depend on the initial system state". This is hard to interpret and without context is limited as a take home point for the reader. I really suggest the authors revise the key points as I take little from them about this study.

\textsf{AR: Fair point. We have modified these points to read\\
"The Community Land Model, version 5, contains numerous modifications to representations of the vegetation carbon and nitrogen cycle.}

\textsf{The control model state, and it's responses to CO$_{2}$ and nitrogen addition are sensitive to parameter choice, but parameter responses are varied between sites that differ in their pre-fertilization water and nitrogen limitation. }

\textsf{Parameters controlling nitrogen fixation rates dominate fertilization responses. Many other fertilization responses are modified indirectly, via changes in the pre-fertilization state. "}

@@

-In general, when the authors talk about "model state" - both in the key points and the abstract - doesn't this require some time context? Are we talking about the equilibrium state? The state at 2019?

\textsf{AR: We have changed this to 'pre-fertilization state' throughout. }

@@

\textsf{AR: Changed to "In CLM4 projections, the inclusion of N dynamics significantly limits the ability of the terrestrial biosphere to ... "}

- Line 52-3: Is that true? Unless that can be supported I would suggest omitting. 
\textsf{AR: We have deleted this section,}

- Line 64: It would be good not to overlook the numerous earlier studies that did actually explore these issues ... e.g. Rastetter et al. (1991) Tree Physiology 9, 101 -126.; Comins \& McMurtrie (1993) Ecological Applications 3, 666-681.; Kirscbaum et al. (1994) Plant, Cell \& Environment, 17: 1081-1099, etc.

\textsf{AR: Thanks for the references. I didn't know about those. We've deleted that section as a way to reframe the introduction to be more general and less focused on the N modifications.**}

@@

- Line 70 onwards. Does this paragraph add anything to the introduction? If anything it is more methods anyway ...

\textsf{AR: OK, we added this part to the methods section. }

- Line 109: Is 1 really a hypothesis as stated?

\textsf{AR: We have modified the hypotheses to be "motivating questions", to re-frame the results and discussion to encompass our intended aims.}

- Line 152: I realise this is more about the LUNA model paper, but I do wonder about the assumption that day length drives variations in photosynthetic capacity, given that you already account for radiation. This just feels like a fudge for a gap in our knowledge as the mechanistic interpretation is less, clear. Anyway, irrelevant I'm sure. 
\textsf{AR: I am inclined to agree, but there's not much that can be done about this issue at this point.}

@@

- Line 163 onwards: In the description of FUN, it would be helpful to provide a little more detail about how much of the cost is parameterised vs emergent. The text is very clear, but I still found myself wanting to know a little more. Obviously I could read the documentation!

\textsf{AR: We added a new sentence to describe the dependence of costs on the environment: \emph{The FUN model, in contrast, employs the principle that for the alternative sources of nitrogen acquisition by plants (active uptake from soil, re-translocation from senescent tissues, and symbiotic N fixation) there is a concurrent cost in terms of carbon (Bloom et al. [1985], Jiang et al. [2017], Terrer et al. [2018]) which is determined by the abundance of nitrogen in the soils and plant tissues and the temperature-dependant cost of N fixation. Within FUN, plants spend excess carbon for nitrogen uptake preferentially using pathways which are `cheaper' to them. Where N is scarce in the environment, carbon that would otherwise have been used for plant growth can be deployed to acquire (pay for) more N. }}

@@

- Line 243: How does the FATES model account for this issue? This seems like it might be an interesting point, but the lack of details means that this statement should either be omitted, or briefly expanded upon.

\textsf{AR: We changed this to: \emph{Newer codes within the CLM framework (e.g. the FATES model, https://github.com/NGEET/fates, \cite{fisher2015}) account for this issue by removing leaves in negative carbon balance.}}

@@

- May I suggest (an optional) text reorganisation? Swap 2.13 and 2.12. Then 2.1.4 follows more logically after the text about FUN for the reader.

\textsf{AR: We have deleted these sections, and reorganized the grouping of the more high-level text that replaces them.}

@@

- Line 509: this is another example where i feel there is too much assumed knowledge by the reader. Having not read Lawrence et al. in review, it is hard to take much from this. Given I know who Lawrence is, I just end up confused how two CLM papers would contradict each other, but lacking the details.

\textsf{AR: The point we're trying to make here is that we find that there is no saturation with increasing leafN content, which is consistent with an analysis in the Lawrence paper that finds low Vcmax compared to observations. We have changed the text to try and make it clearer that this is a point of consensus not contradiction.}

- Overall, I struggled to see what much of the description around parameter sensitivity had to do with the various nutrient assumptions. For example, the text around the Medlyn model could easily be completely omitted. This is true of a number of these parameter paragraphs. Unless there is a link to the nutrient assumptions I fail to see why these details are included? I also think if you dropped some of these irrelevant params, then the plots (fig 6-8) would be easier to interpret.

\textsf{AR: This point is well taken. As we discussed in response to a previous point, we decided to modify the focus of the manuscript to instead illustrate the parameters that are important for the C and N fertilization responses. Further, in light of the need to simplify the discussion and analysis, we have removed 5 of the 13 parameters from the initial version. The reduced range of variation for the Medlyn slope parameter further reduced the impact of that parameter on the output, and therefore less text is expended on its discussion.}

### 2019-07-05 main_revision.tex

\item The control model state, and it's responses to CO$_{2}$ and nitrogen addition are sensitive to parameter choice, but parameter responses are varied across sites and experiments.

\item Parameters controlling nitrogen fixation dominate fertilization responses. Many other fertilization responses are modified indirectly, via changes in the pre-fertilization state. 
\end{keypoints}

@@

Given the large amount of analysis and attention devoted to assessing the impacts of transient CO$_{2}$ and N in the context of global biogeochemical feedback analysis, including the controls on global carbon fertilization `$\beta$' values (the change in ecosystem carbon storage in response to CO$^{2}$ fertilization) (\cite{arora2013}, \cite{friedlingstein2014}), we consider the illustration of how parametric choices in the CLM5 might affect and be responsible for overall behaviour in larger-scale simulations to be an important feature of the documentation of the new model.

@@

Model uncertainty quantification efforts are often framed as an attempt to narrow the parameter space to a small range of 'important' parameters, as-determined by their impact on the model's mean-state predictions (e.g. \cite{dietze2014}, \cite{ricciuto2018}).  Predicted global biogeochemical feedbacks, however, are typically related to the response of the system to forcing, and not necessarily to those system properties that control the mean state. Narrowing the range of variables of interest to those that only impact control states and fluxes (and directing more resources to studying those variables) is thus likely to miss important aspects of transient responses under climate change scenarios.  Similarly, much effort is expended on calibration of models to present-day conditions (\cite{fer2018},\cite{lu2018}, when their responses to climate forcing might be relatively unconstrained by these efforts.  Thus, our motivating hypotheses here are:

1. The parameters that dominate responses to CO$_{2}$ and nitrogen fertilization are distinct from those that control the pre-fertilization model state.

2. There is a trade-off between model parameterizations that allow strong CO$_{2}$ fertilization and those that allow strong N fertilization.

@@

\subsection{Applicability of results to other land surface models}
Our finding that Nitrogen fixation plays a dominant role over responses to $CO_{2}$ fertilization concurs with earlier studies. \cite{wieder2015} investigated the role of two alternative linear models of N fixation within the CLM4.5, while \cite{meyerholt2015} investigate a range of alternative models of N fixation implemented within the O-CN model (\cite{zaehle2010}.

In the CMIP6 generation of land surface models, it is expected that a much greater fraction of model submissions will contain active representations of the terrestrial nitrogen cycle. We propose here that understanding the model parameterizations and structural decisions that contribute to the relative fertilization responses is critical to understanding the implications of the range of results obtained for all models, and that these types of analysis would allow a deeper understanding of land surface model outputs and behaviour. Many further analyses are possible, including global feedback analyses with alternative parameterizations, calibration of critical parameters against manipulation experiments, wider assessment against greater ranges of flux tower data, and tighter constrains of the parameter ranges used. We hope that this initial assessment of the CLM5 parameter space will provide a starting point for such activities.

\subsection{Model improvements highlighted by this analysis}
While there are many potential improvements that could be made to any land surface model, this particular assessment of the parameter space of the CLM5 in this study revealed several dynamics which highlight parts of the representation of biogeochemistry which might be improved in future versions.  Firstly, the response of NPP to increasing \emph{slatop} was often negative, despite increasing GPP, as the fixed-fraction allocation scheme in the model will generate leaves that respire more than they assimilate under very high productivity conditions. This highlights the need for either more realistic tissue allocation, or for a scheme which optimizes leaf allocation to prevent leaf layers in negative carbon balance (\cite{fisher2010}).  Secondly, in other cases, the heuristic C:N stoichiometry algorithm can increase tissue N content in response to environmental forcing in a manner which, again, can act to reduce net assimilation by modifying the balance between assimilation and respiration. In principle, there exists an optimal leaf C:N ratio that maximizes leaf C export under a given set of conditions.  Numerous models of this type have been proposed in the plant optimal functioning literature (\cite{vanwijk2003}, \cite{mcmurtrie2011}, \cite{anten2011} \cite{franklin2012}, \cite{mcmurtrie2013}, \cite{thomas2014}) and future nitrogen cycling model development efforts could re-visit this topic.

Another area requiring focus is the dominance of the 'fraction of fixers' over fertilization responses. \emph{frac\_fixers} is a proxy for the community level composition of nitrogen fixing plants. Technically, because plant density is not represented in the CLM5, this parameter represents the fraction of net assimilated carbon ($gpp$ - $r_{auto}$) that can be used for symbiotic N fixation. Ideally, this feature of the model would be prognostic, and the fraction of N fixing plants would respond to changes in environmental conditions and the relative competitive abilities of N fixing plants. In general, Nitrogen fixers are known to primarily exist in early-successional parts of ecosystems (\cite{vitousek1989}), and therefore representation of their ecological dynamics would likely include a representation of vegetation demographics and succession (\cite{fisher2018vegetation}, \cite{trugman2016climate}).

@@

\subsection{ Methodological Limitations}
Here we investigate the parameter space of the model using step-change experiments. These numerical experiments have the advantage that they can be informed by field experiments (\cite{wieder2019}, however, such experiments necessarily involve unrealistically rapid changes in environmental boundary conditions, and cannot necessarily be considered as analogous to either real-world or transient future scenario conditions.

The development of the CLM5 slightly pre-dated the operational usage of the International Land Model Benchmarking Project (ILAMB) package \cite{collier2018}, \cite{lawrence2018}) for assessing model skill across a very broad range of model components.  In principle, integrating more targeted datasets and data products should narrow the range of model parameter sets that are acceptable in comparison with the suite of available and relevant datasets, as well as accelerate the rejection of model structures that are unrealistic. Ideally, this effort should include synthesis of ecosystem manipulation experiments that provide altered boundary conditions in real life, given the large differences observed here between the sets of parameters affecting present day conditions and those that impact transient responses.

@@

\section{Conclusions}
In this paper we present an analysis of a suite of parameters relevant to vegetation-mediate biogeochemical feedbacks in the extensively modified nitrogen cycle of the Community Land Model, version 5. We illustrate how responses of the model to elevated carbon dioxide and nitrogen deposition might be impacted by parameter choice. We find, in particular, that parameters controlling the degree to which ecosystems can fix additional nitrogen have a dominant effect over responses to fertilization, but limited impacts on the control state. Further, we find that the impact of most parameters is complex and affected by the balance of water, nutrient and other limitations to growth specific to individual sites

It is common practice in land surface modeling literature to present studies that focus on the modification of single aspects of model structure, process representation or calibration, and to highlight the significance of individual modifications when scaled up to global land-mediated climate feedback processes. In this analysis, we illustrate the degree to which a multitude of individual parameters can potentially have important and interacting impacts on model results, how these results differ across sites and output variables and with initial vegetation conditions.  Future studies of process and parameter modification in CLM5 might use these results as a guide to the relative (rather than absolute) importance of individual focus parameters and processes. We thus hope to move forwards from studies that modify individual processes in isolation to those that take a more holistic view of the complexity inherent in modeling coupled land surface systems.

We have attempted here to illustrate and understand the connections between the structure and parameterization of the CLM5 and its biogeochemical functionality. This necessarily complex exercise represents one small part of the assessment of CMIP6-era representations of the land surface needed to understand how advances in model structures alter our predictions of land surface functionality.  The challenges of comprehending, measuring and constraining the parametric and structural uncertainty of increasingly complex process-based and land surface models are daunting. We argue that in order to make progress on this task, the scientific community should move beyond the paradigm of assessing single points in model parameter space in great depth, ignoring all other plausible instantiations. In atmospheric sciences, for example, 'internal variability' caused by initial conditions is now routinely sampled, given its major impact on even long timescale forecasts (\cite{kay2015}). \cite{bonan2018} illustrate how initial conditions are unimportant for carbon cycle prediction on land, relative to structural and parametric uncertainty. Given this, sampling the important dimensions of parametric uncertainty in global Earth system model predictions should be taken seriously during future assessments of biogeochemical feedback strength.

>>>>

\item The control model state, and it's responses to CO$_{2}$ and nitrogen addition are sensitive to parameter choice, but parameter responses are varied between sites that differ in their pre-fertilization water and nitrogen limitation.

\item Parameters controlling nitrogen fixation rates dominate fertilization responses. Many other fertilization responses are modified indirectly, via changes in the pre-fertilization state. 
\end{keypoints}

@@

Given the large amount of analysis and attention devoted to assessing the impacts of transient CO$_{2}$ and N in the context of global biogeochemical feedback analysis, including the controls on global carbon fertilization `$\beta$' values (the change in ecosystem carbon storage in response to CO$_{2}$ fertilization) (\cite{arora2013}, \cite{friedlingstein2014}), we consider the illustration of how parametric choices in the CLM5 might affect and be responsible for overall behaviour in larger-scale simulations to be an important feature of the documentation of the new model.

@@

Model uncertainty quantification efforts are often framed as an attempt to narrow the parameter space to a small range of 'important' parameters, as-determined by their impact on the model's mean-state predictions (e.g. \cite{dietze2014}, \cite{ricciuto2018}).  Predicted global biogeochemical feedbacks, however, are typically related to the response of the system to forcing, and not necessarily to those system properties that control the mean state. Narrowing the range of variables of interest to those that only impact control states and fluxes (and directing more resources to studying those variables) is thus likely to miss important aspects of transient responses under climate change scenarios.  Similarly, much effort is expended on calibration of models to present-day conditions (\cite{fer2018}, \cite{lu2018}, when their responses to climate forcing might be relatively unconstrained by these efforts.  Thus, our motivating questions here are:

1. Are parameters that dominate responses to CO$_{2}$ and nitrogen fertilization also dominant over the pre-fertilization model state?

2. How do fertilization impacts and parameter sensitivities vary with site conditions, as expressed via water and nutrient limitations.

@@

\subsection{Model improvements highlighted by this analysis}
While there are many potential improvements that could be made to any land surface model, this particular assessment of the parameter space of the CLM5 in this study revealed several dynamics which highlight parts of the representation of biogeochemistry which might be improved in future versions.  
Firstly, the response of NPP to increasing \emph{slatop} was often negative, despite increasing GPP, as the fixed-fraction allocation scheme in the model will generate leaves that respire more than they assimilate under very high productivity conditions. This highlights the need for either more realistic tissue allocation, or for a scheme which optimizes leaf allocation to prevent leaf layers in negative carbon balance (\cite{fisher2010}).

Secondly, in other cases, the heuristic C:N stoichiometry algorithm can increase tissue N content in response to environmental forcing in a manner which, again, can act to reduce net assimilation by modifying the balance between assimilation and respiration. In principle, there exists an optimal leaf C:N ratio that maximizes leaf C export under a given set of conditions.  Numerous models of this type have been proposed in the plant optimal functioning literature (\cite{vanwijk2003}, \cite{mcmurtrie2011}, \cite{anten2011} \cite{franklin2012}, \cite{mcmurtrie2013}, \cite{thomas2014}) and future nitrogen cycling model development efforts could re-visit this topic.

Thirdly, requiring focus is the dominance of the 'fraction of fixers' over fertilization responses. \emph{frac\_fixers} is a proxy for the community level composition of nitrogen fixing plants. Technically, because plant density is not represented in the CLM5, this parameter represents the fraction of net assimilated carbon ($gpp$ - $r_{auto}$) that can be used for symbiotic N fixation. Ideally, this feature of the model would be prognostic, and the fraction of N fixing plants would respond to changes in environmental conditions and the relative competitive abilities of N fixing plants. In general, Nitrogen fixers are known to primarily exist in early-successional parts of ecosystems (\cite{vitousek1989}), and therefore representation of their ecological dynamics would likely include a representation of vegetation demographics and succession (\cite{fisher2018vegetation}, \cite{trugman2016climate}).

@@

\subsection{Applicability of results to other land surface models}
Our finding that Nitrogen fixation plays a dominant role over responses to $CO_{2}$ fertilization concurs with earlier studies. Notably, \cite{meyerholt2015} investigate six alternative models of N fixation implemented within the O-CN model (\cite{zaehle2010}). They emphasize that the formulation which, as in CLM5, switches N sources depending on their relative costs, represent a promising means by which N fixation might be simulated. Interestingly, their model also includes a maximum rate of fixation per unit (root) biomass, but analysis to it's sensitivity is not shown. Further, given the difficulty of matching observations of complex N cycle processes with more abstract 'big leaf' models such as CLM5, and the ecological complexities governing the abundance their abundance, \cite{meyerholt2015} also advocate for the dynamic simulation of the distribution of N fixing plants within ESMs, as opposed to the assumption that maximum N fixing capacity if static in space and time.

Given that the response of GPP is almost by definition non-linear with respect to LAI, (given the saturating properties of light absorbtion in increasingly dense canopies) we anticipate that the impacts of initial state will be similar in most land surface models. While it is perhaps not a novel point, the degree of water limitation should act to modulate CO$_{2}$ fertilization while N fertilization will of course be stronger in areas that are more N limited in the first instance.

We find that the model parameters with substantial control over fertilization responses are dissimilar to those with greatest control over the initial model state. However, the CLM5 utilizes a highly simplified fixed-fraction plant allocation scheme, wherein alternative parameterizations can generate very highly divergent ecosystem properties, and further, the allocation fractions are not easily constrained by real-world estimates which vary with plant size. Other models with alternative allocation schemes might not be so sensitive to these parameterizations. Nonetheless, the majority of the parameterizations affecting the transient responses had limited impact on the pre-fertilization state. This suggests that model behaviour in response to rapid change might indeed be time-scale dependent, and perhaps requires further analysis.

\subsection{Caveats and future directions}
Many kinds of further analyses are of course possible, including ramping transient simulations,  including global feedback analyses with alternative parameterizations, calibration of critical parameters against manipulation experiments, wider assessment against greater ranges of flux tower data, and tighter constrains of the parameter ranges used. We hope that this initial assessment of the CLM5 parameter space will provide a starting point for such activities.

Here we investigate the parameter space of the model using step-change experiments. These numerical experiments have the advantage that they can be informed by field experiments (\cite{wieder2019}, however, such experiments necessarily involve unrealistically rapid changes in environmental boundary conditions, and cannot necessarily be considered as analogous to either real-world or transient future scenario conditions.

@@

In principle, integrating more targeted datasets and data products should narrow the range of model parameter sets that are acceptable in comparison with the suite of available and relevant datasets, as well as accelerate the rejection of model structures that are unrealistic.  The development of the CLM5 slightly pre-dated the operational usage of the International Land Model Benchmarking Project (ILAMB) package \cite{collier2018}, \cite{lawrence2018}) for assessing model skill across a very broad range of model components.  Ideally, this effort should include synthesis of ecosystem manipulation experiments that provide altered boundary conditions in real life, given the large differences observed here between the sets of parameters affecting present day conditions and those that impact transient responses.

\section{Conclusions}
In this paper we present an analysis of a suite of parameters relevant to vegetation-mediated biogeochemical feedbacks in the extensively modified Community Land Model, version 5. We illustrate how responses of the model to elevated carbon dioxide and nitrogen deposition might be impacted by parameter choice. We find, in particular, that parameters controlling the degree to which ecosystems can fix additional nitrogen have a dominant effect over responses to fertilization, but limited impacts on the control state. Further, we find that the impact of most parameters is complex and affected by the balance of water, nutrient and other limitations to growth specific to individual sites

It is common practice in land surface modeling literature to present studies that focus on the modification of single aspects of model structure, process representation or calibration, and to highlight the significance of individual modifications when scaled up to global land-mediated climate feedback processes. In this analysis, we illustrate the degree to which a multitude of individual parameters can potentially have important and interacting impacts on model results, how these results differ across sites and output variables and with initial vegetation conditions.  Future studies of process and parameter modification in CLM5 might use these results as a guide to the relative importance of individual focus parameters and processes. We thus hope to move forwards from studies that modify individual processes in isolation to those that take a more holistic view of the complexity inherent in modeling coupled land surface systems.

We have attempted here to illustrate and understand the connections between the structure and parameterization of the CLM5 and its biogeochemical functionality. This necessarily complex exercise represents one small part of the assessment of CMIP6-era representations of the land surface required to understand how advances in model structures alter our predictions of land surface functionality.  The challenges of comprehending, measuring and constraining the parametric and structural uncertainty of increasingly complex process-based and land surface models are daunting. We argue that in order to make progress on this task, the scientific community should move beyond the paradigm of assessing single points in model parameter space in great depth, ignoring all other plausible instantiations. In atmospheric sciences, for example, 'internal variability' caused by initial conditions is now routinely sampled, given its major impact on even long timescale forecasts (\cite{kay2015}). \cite{bonan2018} illustrate how initial conditions are relatively unimportant for carbon cycle prediction on land, relative to structural and parametric uncertainty. Given this, sampling the important dimensions of parametric uncertainty that govern biospheric feedbacks in the climate system should be taken seriously when planning future assessments of biogeochemical feedback strength.
